\subsection{Studying ignored bounty issue reports}
\label{rq4}
\input{rq4}

\subsection{The implications of our findings}
\textbf{Backers should consider proposing a bounty as early as possible and be cautious when proposing small bounties on long-standing issue reports.}
The timing of proposing a bounty is an important factor that impacts the issue-addressing likelihood. In Sections~\ref{rq2} and~\ref{rq3}, we revealed the fact that issue reports for which bounties were proposed earlier are more likely to be addressed. Additionally, we observed that issue reports for which bounties were proposed earlier are more likely to be addressed faster. Backers benefit from the higher issue-addressing likelihood and faster issue-addressing speed by proposing bounties earlier.

In Section~\ref{rq2}, we also noticed a big drop (i.e., from 53.2\% to 30.1\%) of the issue-addressing likelihood when backers proposed bounties on long-standing (i.e., more than half a year) issue reports. This drop might be due to such issue reports having become obsolete or being hard to address.
Since bounties with a value of less than \$100 will not be refunded to the backers if the issue report remains unaddressed, we suggest that backers be cautious when proposing small bounties on long-standing issue reports.

\textbf{Backers should consider proposing a relatively bigger bounty in first-timer bounty-projects.} %In %Section~\ref{rq1}, we observed a positive relationship between the issue-addressing likelihood and the bounty-usage frequency. The global models in Section~\ref{rq3} also show similar results.
Although the issue-addressing likelihood is only 37.4\%  for projects with no bounty-usage experience, the first-timer model in Section~\ref{rq3} shows that the bounty value of an issue report is the most important factor in the first-timer projects, as the issue-addressing likelihood is higher for higher bounty values. The high ratio (2.5) of the bounty value of successful bounty issue reports to the bounty value of failed bounty issue reports also supports this finding.
We suggest that backers of projects with no bounty-usage experience propose higher bounty values for issue reports.


\textbf{Bounty platforms should allow for splittable multi-hunter bounties.}
In addition to a voluntary nature, open source projects have a collaborative nature. Some issues are hard for a developer to address alone. Hence, we encourage developers to work together, especially for issue reports which have a high bounty value (as these issue reports are often harder to address).
However, the current bounty workflow only allows \textbf{one} bounty hunter to claim the bounty, which goes against the collaborative nature of open source. It may also drive the developers, who want to collaboratively address the issue, away because not every participant will get a reward at the end. Therefore, bounty platforms should consider adding the ability for a bounty to be split across multiple hunters to encourage developers to work together on difficult bounty issues.


\textbf{Bounties should be transferable.}
The total value of all addressed-unpaid bounties (\$43,256) is ``frozen'' in Bountysource. In addition, the median number of days between the closing date of the issue report and the date of collecting our data is 372.5,  which means that more than half of the bounties from the ignored bounty issue reports were unclaimed for at least one year. 
By manually examining these 479 addressed-unpaid bounty issue reports, we found 31 cases in which someone reminded the bounty hunter to claim the bounty, however, the reminder was ignored. By reassigning these unclaimed bounties to other issue reports, a larger value could be created for these ``stale'' bounties. For example, Bountysource can suggest and enable backers to assign their long-standing unclaimed bounties to another unaddressed issue report, which has many comments (i.e., people care about it), to encourage developers to address the issue report. Interestingly, we also found suggestions from developers who did not want to receive the bounty but suggested the bounty backers transferring the bounty to other issue reports or to the project as a kind of funding.




